---
title: "Exposure to Background Risk Does Not Affect Giving in the Dictator Game: An Experimental Study."
author: "Sun. Y"
date: "`r Sys.Date()`"
output: 
  html_document:
    keep_md: true 
    # having a floating table of content with a depth of 4
    toc: true
    toc_float: 
      collapsed: true
      smooth_scroll: true
    toc_depth: 4
    # section numbering 
    number_sections: true
    # table printing style
    df_print: paged
    # show code chunk as needed
    code_folding: hide
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data Manipulation {.unnumbered}
```{r data clearing & manipulation}
# ============================= loading packages ============================= #
pacman::p_load(
  # data manipulation
  tidyverse, dplyr, readxl, 
  # summary and plots
  ggplot2, scales, xtable, jtools, broom.mixed, 
  # tests and regression
  rcompanion, DescTools, dunn.test, conover.test, aod, corrplot, censReg, sandwich, lmtest, crch, miscTools, caret, mfx, pscl, broom, oglmx, stargazer, magrittr, texreg
  )
path2data <- "G:/My Drive/Projects/Giving under BR/R.markdown/data.csv"
mydata <- as_tibble(read.csv(path2data, header = TRUE)) %>% 
  mutate(br_trts = as.logical(ifelse(dict_treatment == 0, FALSE, TRUE)))
  
# ============================= manipulating data ============================ #
dict_by_trt <- mydata %>%
  dplyr::filter(dict_id_in_group == 1) %>% 
  dplyr::select(
    session, session_date, participant, dict_treatment, dict_ans_check, dict_group_give, dict_gachter_circles, bret_boxes_collected, 
    svo_mean_self:svo_classification, risque_general:experiment_participation
    ) %>% 
  dplyr::rename(
    "date"                 = "session_date",
    "treatment"            = "dict_treatment", 
    "understanding"        = "dict_ans_check", 
    "donation"             = "dict_group_give", 
    "ios"                  = "dict_gachter_circles", 
    "bret"                 = "bret_boxes_collected", 
    "avg_svo(self)"        = "svo_mean_self", 
    "avg_svo(other)"       = "svo_mean_other", 
    "svo"                  = "svo_score", 
    "ra_general"           = "risque_general", 
    "ra_health"            = "risque_sante", 
    "ra_wealth"            = "risque_argent", 
    "trust_others"         = "confiance_autres", 
    "trust_others_general" = "confiance_autres_general", 
    "trust_family"         = "confiance_autres_famille", 
    "trust_work"           = "confiance_autres_travail", 
    "birth_year"           = "year_of_birth", 
    "political"            = "politique"
    ) %>%
  dplyr::mutate(
    date = as.Date(date),
    covid = as.logical(ifelse(date < "2023-01-01", TRUE, FALSE)), 
    session_year = as.numeric(format(as.Date(date, format="%Y%m/%d/"),"%Y")),
          # ================== giving behaviors ==================== # 
    zero_giving = as.logical(ifelse(donation == 0, TRUE, FALSE)), 
    qtr_split = as.logical(ifelse(donation == 5, TRUE, FALSE)), 
    fair_split = as.logical(ifelse(donation == 10, TRUE, FALSE)), 
    little = as.logical(ifelse(donation==5 | donation==6, TRUE, FALSE)),
          # ===================== treatments ======================= # 
    treatment = factor(
      case_when(
        treatment == 0 ~ "ctrl", 
        treatment == 1 ~ "dictator_exp", 
        treatment == 2 ~ "recipient_exp", 
        treatment == 3 ~ "common_exp"
        ),
      levels = c("ctrl", "dictator_exp", "recipient_exp", "common_exp")
      ),
    br_trts = as.logical(ifelse(treatment == "ctrl", FALSE, TRUE)),
    exposure = factor(
      case_when(
        treatment == "ctrl" ~ "ctrl",
        treatment == "dictator_exp" | treatment == "recipient_exp" ~ "one_sided_exp",
        treatment == "common_exp" ~ "common_exp"),
      levels = c("ctrl", "one_sided_exp", "common_exp")
    ),
    one_sided_exposure = as.logical(case_when(
      treatment == "dictator_exp" | treatment == "recipient_exp" ~ TRUE,
      treatment == "ctrl" ~ FALSE, 
      treatment == "common_exp" ~ NA
    )),
          # ======================== svo =========================== # 
    svo_type = factor(
      svo_classification, 
      levels = c("individualist", "competitive", "prosocial", "altruist")
      ),
          # ==================== risk aversion ===================== # 
    ra_bret = 100 - bret, # The higher `ra_bret` gets, the more one is risk averse 
    crra = -bret/(-100 + bret), # converted to CRRA index (Crosetto & Filippin, 2013)
    ra_general = as.numeric(10 - ra_general), # The higher `ra_general` gets, the more one is risk averse
    ra_wealth = as.numeric(10 - ra_wealth), # The higher `ra_wealth` gets, the more one is risk averse w.r.t financial situation
          # ====================== education ======================= #    
    student = as.logical(ifelse(student == "True", TRUE, FALSE)),
    study.level = as.numeric(study_level), 
    study_level = factor(
      case_when(
        as.integer(study_level) == 0 ~ "high_school",
        as.integer(study_level) == 1 | as.integer(study_level) == 2 | as.integer(study_level) == 3 ~ "bachelor",
        as.integer(study_level) == 4 | as.integer(study_level) == 5 ~ "master",
        as.integer(study_level) == 6 | as.integer(study_level) == 7 ~ "phd"),
      levels = c("high_school", "bachelor", "master", "phd")
      ),
    econ = as.logical(
      ifelse(
        # econ related disciplines include "business school"(3), "economics"(6) and "management"(9)
        study_discipline == 3 | study_discipline == 6 | study_discipline == 9, TRUE, FALSE)
      ),
          # ================== demographic info ================== #
    age = session_year - as.numeric(birth_year),
    female = as.logical(ifelse(gender == 0, TRUE, FALSE)), # female if 0 and male otherwise
    marital_status = factor(case_when(
      marital_status == 0 ~ "single", 
      marital_status == 1 ~ "pacsé(e)",
      marital_status == 2 ~ "married", 
      marital_status == 3 ~ "divorced", 
      marital_status == 4 ~ "widowed"),
      levels = c("single", "pacsé(e)", "married", "divorced", "widowed")
      ),
          # ================ political preference ================ #
    political.pref = as.numeric(political),
    political_pref = factor(
      # "neutral" (ref) if 4~6, "left" if 0~3 and "right" if 7~10
      ifelse(political >= 4 & political <= 6, "neutral", ifelse(political < 4, "left", "right")),
      levels = c("neutral", "left", "right")
      )) %>% 
  group_by(treatment)

        # ========== McFadden's pseudo R-squared for tobit =========== #
pseudoR2.tobit <- function(obj) 1 - as.vector(logLik(obj)/logLik(update(obj, . ~ 1))) # PseudoR2() in 'DescTools' does not recognize "censReg" subject

        # ========================= sig. lvl ========================= #
alpha <- .05

# ================================ cleaning ================================== #
remove(path2data)
```
# Predictions

***

**HYPOTHSIS 1**

Risk-neutral dictators with an \textit{ex ante} view on inequality aversion are unaffected by exposure to additive, zero-mean background risk.

***

***

**HYPOTHSIS 2**

One-sided exposure (i.e., Treatments \textit{R_Exp} and \textit{D_Exp}) to additive and zero-mean background risk yields identical and nonpositive effects on FS donations, while common exposure (i.e., Treatment \textit{C_Exp}) has no effect, such that $$ d_{FS}^{\textit{D_Exp}}=d_{FS}^{\textit{R_Exp}}\leq d_{FS}^{\textit{C_Exp}}=d_{FS}^{\textit{No_Exp}} $$

***

***

**HYPOTHSIS 3**

One-sided exposure (i.e., Treatments \textit{R_Exp} and \textit{D_Exp}) to additive and zero-mean background risk has opposite effects on BO donations. Specifically, the recipients' exposure (resp. the dictators' exposure) yields nonnegative (resp. nonpositive) effects on BO donations, such that $$ d_{BO}^{\textit{D_Exp}}\leq d_{BO}^{\textit{No_Exp}}\leq d_{BO}^{\textit{R_Exp}} $$
Meanwhile common exposure (i.e., Treatment \textit{C_Exp}) yield nonnegative effects, such that $$ d_{BO}^{\textit{C_Exp}}\geq d_{BO}^{\textit{No_Exp}} $$

***

# Descriptive Statistics
```{r summary}
summary_trt <- dict_by_trt %>%
  summarise(
    N = n(),
    Mean = round(mean(donation), 2),
    SD = round(sd(donation), 2),
    # median = round(median(donation), 2),
    Zero_giving = percent(sum(zero_giving == TRUE)/n(), accuracy = 0.01),
    Fair_splitting = percent(sum(fair_split == TRUE)/n(), accuracy = 0.01),
    ) %>%
  mutate(
    treatment = case_when(
      treatment == "ctrl" ~ "T0",
      treatment == "dictator_exp" ~ "T1",
      treatment == "recipient_exp" ~ "T2",
      treatment == "common_exp" ~ "T1&2",
      TRUE ~ as.character(treatment)
    )
  )
summary_trt
```
```{r nonparametric tests}
round.digits <- 4

# ============================ ON DONATION AMOUNTS =========================== #     
        # ======== kruskal-wallis rank sum test: r_exp & d_exp ======= #                
kruskal.wallis_r_exp_d_exp <- kruskal.test(
  formula = donation ~ treatment,
  data = dict_by_trt %>% filter(treatment != "common_exp")
)             

        # ========== two-sided wilcoxon rank sum test: c_exp ========= # 
mw_c_exp <- wilcox.test(
  x = (dict_by_trt %>% filter(treatment == "common_exp")) %>% pull(donation),
  y = (dict_by_trt %>% filter(treatment == "ctrl")) %>% pull(donation),
  alternative = "two.sided",
  # alternative = "less", # `fs_no_exp_c_exp`: `common_exp` yields a negative effect
  paired = FALSE)

        # ====== kruskal-wallis rank sum test: all trts ====== #
kruskal.wallis_trts <- kruskal.test(
  formula = donation ~ treatment, data = dict_by_trt
  )

# ============================ ON GIVING BEHAVIORS =========================== #
baseline <- "ctrl"
giving.behaviors <- c("zero_giving", "fair_split")
treatment.groups <- c("dictator_exp", "recipient_exp", "common_exp")
for (giving in giving.behaviors) {
  for (trt in treatment.groups) {
        # ====================== chi-square test ===================== #               
    chisq <- paste("chisq", giving, trt, sep = "_")
    assign(chisq,
           chisq.test(
             x = dict_by_trt %>% filter(treatment == baseline | treatment == trt) %>% pull(treatment),
             y = dict_by_trt %>% filter(treatment == baseline | treatment == trt) %>% pull(!!giving)
             )
           )
        # ==================== fisher's exact test =================== #
    fisher <- paste("fisher", giving, trt, sep = "_")
    assign(fisher,
           fisher.test(
             x = dict_by_trt %>% filter(treatment == baseline | treatment == trt) %>% pull(treatment),
             y = dict_by_trt %>% filter(treatment == baseline | treatment == trt) %>% pull(!!giving)
             )
           )
  }
}

# ================================== SUMMARY ================================= #
summary_donation <- data.frame(
  comparison = c("T0_vs_(T1_T2)", "T0_vs_T1&2", "T0_vs_(T1_T2_T1&2)"),
  tests = c(
    kruskal.wallis_r_exp_d_exp$method, mw_c_exp$method, kruskal.wallis_trts$method
  ),
  statistics = c(
    kruskal.wallis_r_exp_d_exp$statistic, mw_c_exp$statistic, kruskal.wallis_trts$statistic
  ),
  df = c(
    kruskal.wallis_r_exp_d_exp$parameter, NA, kruskal.wallis_trts$parameter
  ),
  p.value = c(
    kruskal.wallis_r_exp_d_exp$p.value, mw_c_exp$p.value, kruskal.wallis_trts$p.value
  )
) %>% mutate(
    across(where(is.numeric), ~ format(round(., digits = round.digits), nsmall = round.digits, scientific = FALSE)),
    significance = case_when(
      p.value >= 0.1 ~ "None",
      p.value >= 0.05 & p.value < 0.1 ~ "*",
      p.value >= 0.01 & p.value < 0.05 ~ "**",
      p.value < 0.01 ~ "***"
    )
)
summary_donation

summary_zero <- data.frame(
  zero_giving = c("T0_vs_T1", 
                  "T0_vs_T2", 
                  "T0_vs_T1&2"),
  chisq.statistic = c(chisq_zero_giving_dictator_exp$statistic,
                      chisq_zero_giving_recipient_exp$statistic,
                      chisq_zero_giving_common_exp$statistic), 
  chisq.df = c(chisq_zero_giving_dictator_exp$parameter, 
               chisq_zero_giving_recipient_exp$parameter, 
               chisq_zero_giving_common_exp$parameter),
  chisq.p = c(chisq_zero_giving_dictator_exp$p.value, 
              chisq_zero_giving_recipient_exp$p.value, 
              chisq_zero_giving_common_exp$p.value),
  fisher.p = c(fisher_zero_giving_dictator_exp$p.value, 
               fisher_zero_giving_recipient_exp$p.value, 
               fisher_zero_giving_common_exp$p.value)
) %>% mutate(
    across(where(is.numeric), ~ format(round(., digits = round.digits), nsmall = round.digits, scientific = FALSE))
)
summary_zero

summary_fair <- data.frame(
  fair_giving = c("T0_vs_T1", 
                  "T0_vs_T2", 
                  "T0_vs_T1&2"),
  chisq.statistic = c(chisq_fair_split_dictator_exp$statistic, 
                       chisq_fair_split_recipient_exp$statistic, 
                       chisq_fair_split_common_exp$statistic), 
  chisq.df = c(chisq_fair_split_dictator_exp$parameter, 
               chisq_fair_split_recipient_exp$parameter, 
               chisq_fair_split_common_exp$parameter),
  chisq.p = c(chisq_fair_split_dictator_exp$p.value, 
              chisq_fair_split_recipient_exp$p.value, 
              chisq_fair_split_common_exp$p.value),
  fisher.p = c(fisher_fair_split_dictator_exp$p.value, 
               fisher_fair_split_recipient_exp$p.value, 
               fisher_fair_split_common_exp$p.value)
) %>% mutate(
    across(where(is.numeric), ~ format(round(., digits = round.digits), nsmall = round.digits, scientific = FALSE))
)
summary_fair
```
# Regression Analysis
## Donation amounts (Tobit)
```{r type-I tobit left-censored at zero}
# NOTE: coeftest() is only for facilitating the p correction
# ============================== SPECIFIICATION ============================== #
tobit_br <- censReg(
  formula = donation ~ br_trts, 
  data = dict_by_trt, left = 0
)
tobit_trt <- censReg(
  formula = donation ~ treatment, 
  data = dict_by_trt, left = 0
)
tobit_bret_svo <- censReg(
  formula = donation ~ treatment + ra_bret + svo,
  # formula = donation ~ treatment + ra_bret + svo + female + study.level,
  data = dict_by_trt, left = 0
)
tobit_int <- censReg(
  formula = donation ~ treatment * ra_bret + svo,
  # formula = donation ~ treatment * ra_bret + svo + female + study.level,
  data = dict_by_trt, left = 0
)
tobit_ctrl <- censReg(
  formula = donation ~ treatment + ra_bret + svo + female + study.level,
  data = dict_by_trt, left = 0
)
```
```{r p correction (tobit)}
selected.tobit <- c("tobit_br", "tobit_trt", "tobit_bret_svo", "tobit_int", "tobit_ctrl")
for (model in selected.tobit) {
  tobit_coeftest <- paste(model, "_coeftest", sep = "") 
  assign(
    tobit_coeftest,
    coeftest(get(model))
    )
  pseudoR2 <- paste("pseudoR2_", model, sep = "")
  assign(
    pseudoR2, 
    round(pseudoR2.tobit(get(model)), 3)
  )
  logLik <- paste("logLik_", model, sep = "")
  assign(
    logLik,
    logLik(get(model))[1]
  )
}

# ================= BONFERRONI CORRECTION FOR FALSE POSITIVE ================= #
selected.method = "bonferroni"
        # ================ `tobit_trt` ================ #
adjusted.p <- p.adjust(
  p = as.numeric(tobit_trt_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- tobit_trt_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
tobit_trt_p.adj <- temp
# tobit_trt_p.adj
        # ============ `tobit_bret_svo` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(tobit_bret_svo_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- tobit_bret_svo_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
tobit_bret_svo_p.adj <- temp
# tobit_bret_svo_p.adj
        # ================ `tobit_int` ================ #
adjusted.p <- p.adjust(
  p = as.numeric(tobit_int_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp", "treatmentdictator_exp:ra_bret", "treatmentrecipient_exp:ra_bret", "treatmentcommon_exp:ra_bret"),4]),
  method = selected.method
  )
temp <- tobit_int_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp", "treatmentdictator_exp:ra_bret", "treatmentrecipient_exp:ra_bret", "treatmentcommon_exp:ra_bret"),4] <- adjusted.p
tobit_int_p.adj <- temp
# tobit_int_p.adj
        # =============== `tobit_ctrl` ================ #
adjusted.p <- p.adjust(
  p = as.numeric(tobit_ctrl_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- tobit_ctrl_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
tobit_ctrl_p.adj <- temp
# tobit_ctrl_p.adj

# ================================= CLEANING ================================= #
remove(list = ls(pattern = "_coeftest$"))
remove(list = c("selected.tobit", "model", "pseudoR2", "logLik", "selected.method", "temp", "adjusted.p"))
```
```{r summary: left-censored tobit}
# NOTE: regression statistics are only available when the original models are used directly in screenreg().

screenreg(
  l = list(
    tobit_trt_p.adj,                                        # (1)
    tobit_bret_svo_p.adj,                                   # (2)
    tobit_int_p.adj,                                        # (3)
    tobit_ctrl_p.adj                                        # (4)
    ),
  # custom.header = list("Donation amount in DG" = 1:5),
  custom.header = list("Donation amount in DG (Tobit)" = 1:4),
  custom.model.names = c(
    "(1)",                                                  # (1)
    "(2)",                                                  # (2)
    "(3)",                                                  # (3)
    "(4)"                                                   # (4)
  ),
  custom.coef.names = c("T1", "T2", "T1&2", "Risk_Aversion (RA)", "SVO", "T1 × RA", "T2 × RA", "T1&2 × RA", "Female", "Study_Lvl"),
  omit.coef = "logSigma|(Intercept)",
  digits = 3,
  stars = c(0.01, 0.05, 0.1),
  custom.note = "* p<0.1; ** p<0.05; *** p<0.01. P-values associated with the treatments are adjusted using Bonferroni method."
)
```
## Zero-giving & Fair-splitting
```{r probit with zero_giving & fair_split}
# ============================== SPECIFIICATION ============================== #
        # ====================== ZERO-GIVING ====================== #
probit_zero_br <- glm(
  formula = zero_giving ~ br_trts,
  family = binomial(link = probit), data = dict_by_trt
  )
probit_zero_trt <- glm(
  formula = zero_giving ~ treatment,
  family = binomial(link = probit), data = dict_by_trt
  )
probit_zero_int <- glm(
  formula = zero_giving ~ treatment * ra_bret + svo,
  family = binomial(link = probit), data = dict_by_trt
  )
probit_zero_ctrl <- glm(
  formula = zero_giving ~ treatment + ra_bret + svo + female,
  family = binomial(link = probit), data = dict_by_trt
  )
        # ==================== FAIR-SPLITTING ==================== #
probit_fair_br <- glm(
  formula = fair_split ~ br_trts,
  family = binomial(link = probit), data = dict_by_trt
  )
probit_fair_trt <- glm(
  formula = fair_split ~ treatment,
  family = binomial(link = probit), data = dict_by_trt
  )
probit_fair_int <- glm(
  formula = fair_split ~ treatment * ra_bret + svo,
  family = binomial(link = probit), data = dict_by_trt
  )
probit_fair_ctrl <- glm(
  formula = fair_split ~ treatment + ra_bret + svo + female,
  family = binomial(link = probit), data = dict_by_trt
  )
```
```{r p correction (probit: zero_giving & fair_split)}
selected.probit <- c(
  "probit_zero_br", "probit_zero_trt", "probit_zero_int", "probit_zero_ctrl", 
  "probit_fair_br", "probit_fair_trt", "probit_fair_int", "probit_fair_ctrl"
  )
for (model in selected.probit) {
  probit_coeftest <- paste(model, "_coeftest", sep = "") 
  assign(
    probit_coeftest,
    coeftest(get(model))
    )
  mfx.probit <- paste("mfx_", model, sep = "")
  assign(
    mfx.probit,
    probitmfx(
      get(model), 
      data = dict_by_trt, atmean = FALSE
      )
  )
  # compute other statistics of the regression: McFadden's pseudo R-squared, Log likelihood
  pseudoR2 <- paste("pseudoR2_", model, sep = "")
  assign(
    pseudoR2, 
    PseudoR2(
      get(model),
      which = "McFadden"
      )
    )
  logLik <- paste("logLik_", model, sep = "")
  assign(
    logLik,
    logLik(get(model))[1]
    )
}

# ================= BONFERRONI CORRECTION FOR FALSE POSITIVE ================= #
selected.method = "bonferroni"

        # ============ `probit_zero_trt` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(probit_zero_trt_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- probit_zero_trt_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
probit_zero_trt_p.adj <- temp
# probit_zero_trt_p.adj
        # ============ `probit_fair_trt` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(probit_fair_trt_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- probit_fair_trt_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
probit_fair_trt_p.adj <- temp
# probit_fair_trt_p.adj
        # ============ `probit_zero_ctrl` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(probit_zero_ctrl_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- probit_zero_ctrl_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
probit_zero_ctrl_p.adj <- temp
# probit_zero_ctrl_p.adj
        # ============ `probit_fair_ctrl` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(probit_fair_ctrl_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4]),
  method = selected.method
  )
temp <- probit_fair_ctrl_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp"),4] <- adjusted.p
probit_fair_ctrl_p.adj <- temp
# probit_fair_ctrl_p.adj
        # ============ `probit_zero_int` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(probit_zero_int_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp", "treatmentdictator_exp:ra_bret", "treatmentrecipient_exp:ra_bret", "treatmentcommon_exp:ra_bret"),4]),
  method = selected.method
  )
temp <- probit_zero_int_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp", "treatmentdictator_exp:ra_bret", "treatmentrecipient_exp:ra_bret", "treatmentcommon_exp:ra_bret"),4] <- adjusted.p
probit_zero_int_p.adj <- temp
# probit_zero_int_p.adj
        # ============ `probit_fair_int` =============== #
adjusted.p <- p.adjust(
  p = as.numeric(probit_fair_int_coeftest[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp", "treatmentdictator_exp:ra_bret", "treatmentrecipient_exp:ra_bret", "treatmentcommon_exp:ra_bret"),4]),
  method = selected.method
  )
temp <- probit_fair_int_coeftest
temp[c("treatmentdictator_exp", "treatmentrecipient_exp", "treatmentcommon_exp", "treatmentdictator_exp:ra_bret", "treatmentrecipient_exp:ra_bret", "treatmentcommon_exp:ra_bret"),4] <- adjusted.p
probit_fair_int_p.adj <- temp
# probit_fair_int_p.adj

# ================================= CLEANING ================================= #
remove(list = ls(pattern = "_coeftest$"))
remove(list = c("selected.probit", "model", "pseudoR2", "logLik", "selected.method", "temp", "adjusted.p"))
```
```{r summary: probit (zero-giving & fair-splitting)}
# ============= REGRESSION SUMMARY TABLE 1: PO, OLS, AND TOBIT =============== #
screenreg(
  l = list(
    probit_zero_trt_p.adj,                                  # (1)
    probit_zero_int_p.adj,                                  # (2)
    probit_zero_ctrl_p.adj,                                 # (3)
    probit_fair_trt_p.adj,                                  # (4)
    probit_fair_int_p.adj,                                  # (5)
    probit_fair_ctrl_p.adj                                  # (6)
    ),
  custom.header = list("Pr(zero-giving|X)" = 1:3, "Pr(fair_splitting|X)" = 4:6),
  custom.model.names = c(
    "(1)",                                                  # (1)
    "(2)",                                                  # (2)
    "(3)",                                                  # (3)
    "(4)",                                                  # (4)
    "(5)",                                                  # (5)
    "(6)"                                                   # (6)
  ),
  custom.coef.names = c("T1", "T2", "T1&2", "Risk_Aversion (RA)", "SVO", "T1 × RA", "T2 × RA", "T1&2 × RA", "Female"),
  omit.coef = "(Intercept)",
  digits = 3,
  stars = c(0.01, 0.05, 0.1),
  custom.note = "* p<0.1; ** p<0.05; *** p<0.01. P-values associated with the treatments are adjusted using Bonferroni method."
)

```
# Exploratory analysis
## Covid effect
```{r covid effect, warning=FALSE}
# ============================= contingency table ============================ #
treatment.group <- c("ctrl", "dictator_exp", "recipient_exp", "common_exp")

contingency_obs_covid <- as.data.frame.matrix(
  table(dict_by_trt$treatment, dict_by_trt$covid)
  ) %>%
  `colnames<-`(c("after.covid_obs", "during.covid_obs")) %>%
  `rownames<-`(c("T0", "T1", "T2", "T1&2"))

summary_giving_covid <- data.frame(
  treatments = c("T0", "T1", "T2", "T1&2"),
  during.covid = c(round(mean((dict_by_trt %>% filter(treatment == "ctrl" & covid == TRUE)) %>% pull(donation)), 2), 
                   round(mean((dict_by_trt %>% filter(treatment == "dictator_exp" & covid == TRUE)) %>% pull(donation)), 2),
                   round(mean((dict_by_trt %>% filter(treatment == "recipient_exp" & covid == TRUE)) %>% pull(donation)), 2),
                   round(mean((dict_by_trt %>% filter(treatment == "common_exp" & covid == TRUE)) %>% pull(donation)), 2)),
  after.covid = c(round(mean((dict_by_trt %>% filter(treatment == "ctrl" & covid != TRUE)) %>% pull(donation)), 2), 
                   round(mean((dict_by_trt %>% filter(treatment == "dictator_exp" & covid != TRUE)) %>% pull(donation)), 2),
                   round(mean((dict_by_trt %>% filter(treatment == "recipient_exp" & covid != TRUE)) %>% pull(donation)), 2),
                   round(mean((dict_by_trt %>% filter(treatment == "common_exp" & covid != TRUE)) %>% pull(donation)), 2))
  ) %>%
  rename_with( ~ "Mean", .cols = 1)

# =============================== covid effect =============================== #
for (trt in treatment.group) {
  mw <- paste("mw_", trt, sep = "")
  assign(mw,
         wilcox.test(
           x = (dict_by_trt %>% filter(treatment == trt & covid == TRUE)) %>% pull(donation), 
           y = (dict_by_trt %>% filter(treatment == trt & covid != TRUE)) %>% pull(donation), 
           alternative = "two.sided", 
           paired = FALSE)
         )
  mw_ties <- paste("mw_", trt, "_ties", sep = "")
  assign(mw_ties,
         coin::wilcox_test(
           donation ~ factor(covid), 
           data = dict_by_trt[dict_by_trt$treatment == trt, ],
           alternative = "two.sided", 
           paired = FALSE)
         )
}

# =========================== local chunk summary ============================ #
contingency_obs_covid[, c(2, 1)] # swap the original 1st and 2nd columns (putting "during covid" forward) 

summary_giving_covid

donation_covid.effect <- data.frame(
  donation_covid.effect = c("T0", "T1", "T2", "T1&2"),
  statistic_mw = c(mw_ctrl$statistic, 
                   mw_dictator_exp$statistic, 
                   mw_recipient_exp$statistic, 
                   mw_common_exp$statistic),
  p.value_mw = c(mw_ctrl$p.value, 
                 mw_dictator_exp$p.value, 
                 mw_recipient_exp$p.value, 
                 mw_common_exp$p.value)
)
donation_covid.effect
```

## IOS scale
```{r ios scale}
# ================================= SUMMARY ================================== #
summary_dictator_ios_trt <- mydata %>% 
  group_by(dict_treatment) %>% 
  filter(dict_id_in_group == 1) %>% # dictators only
  drop_na(dict_gachter_circles) %>% 
  summarise(
    obs = n(),
    mean_dictator = round(mean(dict_gachter_circles), 2),
    sd_dictator = round(sd(dict_gachter_circles), 2)
    # median = round(median(dict_gachter_circles), 2)
    ) %>%
  mutate(
    dict_treatment = case_when(
      dict_treatment == 0 ~ "T0",
      dict_treatment == 1 ~ "T1",
      dict_treatment == 2 ~ "T2",
      dict_treatment == 3 ~ "T1&2",
      TRUE ~ as.character(dict_treatment)
    )
  ) %>%
  rename_with( ~ "treatment", .cols = 1)
summary_dictator_ios_trt

summary_recipient_ios_trt <- mydata %>% 
  group_by(dict_treatment) %>% 
  filter(dict_id_in_group == 2) %>% # dictators only
  drop_na(dict_gachter_circles) %>% 
  summarise(
    obs = n(),
    mean_recipient = round(mean(dict_gachter_circles), 2),
    sd_recipient = round(sd(dict_gachter_circles), 2)
    # median = round(median(dict_gachter_circles), 2)
    ) %>%
  mutate(
    dict_treatment = case_when(
      dict_treatment == 0 ~ "T0",
      dict_treatment == 1 ~ "T1",
      dict_treatment == 2 ~ "T2",
      dict_treatment == 3 ~ "T1&2",
      TRUE ~ as.character(dict_treatment)
    )
  ) %>%
  rename_with( ~ "treatment", .cols = 1)
summary_recipient_ios_trt

# ================================ SAMPLE SIZE =============================== #
# nrow(dict_by_trt %>% drop_na(ios))

# ================================ CORRELATION =============================== #
cor_svo_ios <- cor.test(
  dict_by_trt %>% drop_na(ios) %>% pull(svo), 
  dict_by_trt %>% drop_na(ios) %>% pull(ios)
  )
# cor_svo_ios

pearson_donation_ios <- cor.test(
  dict_by_trt %>% drop_na(ios) %>% pull(donation), 
  dict_by_trt %>% drop_na(ios) %>% pull(ios)
  )
cor_donation_ios <- data.frame(
  correlation = pearson_donation_ios$method,
  r = pearson_donation_ios$estimate,
  df = as.character(pearson_donation_ios$parameter),
  statistic = pearson_donation_ios$statistic,
  p = pearson_donation_ios$p.value
) %>% mutate(
    across(where(is.numeric), ~ format(round(., digits = 5), nsmall = 5, scientific = FALSE))
)
cor_donation_ios
```

```{r tobit (donation~ios)}
# =========================== TOBIT: DONATION ~ IOS ========================== #
tobit_donation_ios <- censReg(
  formula = donation ~ ios + svo, left = 0,
  data = dict_by_trt %>% drop_na(ios)
)
tobit_donation_ios_coeftest <- coeftest(tobit_donation_ios)

# ================= TOBIT: ZERO-GIVING / FAIR-SPLITTING ~ IOS ================ #
probit_zero_ios <- glm(
  formula = zero_giving ~ ios + svo, family = binomial(link = probit), 
  data = dict_by_trt %>% drop_na(ios)
  )

probit_fair_ios <- glm(
  formula = fair_split ~ ios + svo, family = binomial(link = probit), 
  data = dict_by_trt %>% drop_na(ios)
  )

selected.probit <- c("probit_zero_ios", "probit_fair_ios")
for (model in selected.probit) {
  probit_coeftest <- paste(model, "_coeftest", sep = "") 
  assign(
    probit_coeftest,
    coeftest(get(model))
    )
}

# =========================== MCFADDEN'S PSEUDO R2 =========================== #
pseudoR2_tobit_donation_ios <- round(pseudoR2.tobit(tobit_donation_ios), 3)
pseudoR2_probit_zero_ios <- round(PseudoR2(probit_zero_ios), 3)
pseudoR2_probit_fair_ios <- round(PseudoR2(probit_fair_ios), 3)

# ============================== LOG LIKELIHOOD ============================== #
# logLik_tobit_donation_ios <- logLik(tobit_donation_ios)[1]

# ============================ REGRESSION SUMMARY ============================ #
screenreg(
  l = list(
    tobit_donation_ios,                                     # (1)
    probit_zero_ios,                                        # (2)
    probit_fair_ios                                         # (3)
    ),
  custom.header = list("Donation" = 1, "Zero-giving" = 2, "Fair-splitting" = 3),
  custom.model.names = c(
    "(1)",                                                  # (1)
    "(2)",                                                  # (2)
    "(3)"                                                   # (3)
  ),
  custom.coef.names = c("(Intercept)", "IOS", "SVO", "logSigma"),
  omit.coef = "logSigma|(Intercept)",
  digits = 3,
  stars = c(0.01, 0.05, 0.1),
  custom.note = "* p<0.1; ** p<0.05; *** p<0.01."
)
```
```{r nonparametric tests (ios)}
mw_ios_dictator_recipient <- wilcox.test(
  x = mydata %>% drop_na(dict_gachter_circles) %>% filter(dict_id_in_group == 1) %>% pull(dict_gachter_circles), # dictators' ios
  y = mydata %>% drop_na(dict_gachter_circles) %>% filter(dict_id_in_group == 2) %>% pull(dict_gachter_circles), # recipients' ios
  alternative = "two.sided",
  paired = FALSE)

kruskal.wallis_ios_dictator_trts <- kruskal.test(
  formula = dict_gachter_circles ~ dict_treatment, data = mydata %>% drop_na(dict_gachter_circles) %>% filter(dict_id_in_group == 1)
  )

kruskal.wallis_ios_recipient_trts <- kruskal.test(
  formula = dict_gachter_circles ~ dict_treatment, data = mydata %>% drop_na(dict_gachter_circles) %>% filter(dict_id_in_group == 2)
  )

# ================================== SUMMARY ================================= #
round.digits <- 4

summary_ios <- data.frame(
  comparison = c("dictators' ios_vs_recipients' ios", "dictators' ios_trt", "recipients' ios_trt"),
  tests = c(
    mw_ios_dictator_recipient$method, kruskal.wallis_ios_dictator_trts$method, kruskal.wallis_ios_recipient_trts$method
  ),
  statistics = c(
    mw_ios_dictator_recipient$statistic, kruskal.wallis_ios_dictator_trts$statistic, kruskal.wallis_ios_recipient_trts$statistic
  ),
  df = c(
    NA, as.character(kruskal.wallis_ios_dictator_trts$parameter), as.character(kruskal.wallis_ios_recipient_trts$parameter)
  ),
  p.value = c(
    mw_ios_dictator_recipient$p.value, kruskal.wallis_ios_dictator_trts$p.value, kruskal.wallis_ios_recipient_trts$p.value
  )
) %>% mutate(
    across(where(is.numeric), ~ format(round(., digits = round.digits), nsmall = round.digits, scientific = FALSE)),
    significance = case_when(
      p.value >= 0.1 ~ "None",
      p.value >= 0.05 & p.value < 0.1 ~ "*",
      p.value >= 0.01 & p.value < 0.05 ~ "**",
      p.value < 0.01 ~ "***"
    )
)
summary_ios
```